IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2020-10-08 main.tex
:art: Rephrase problem formulation

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation. Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Wu2019}. Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting.	In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel through each reflector with the others switched off. To reduce estimation overhead and design complexity, \cite{Yang2019} exploited the spatial correlation and proposed a group-based IRS model where adjacent elements share a common reflection coefficient. Recent research also explored the possibility of integrating IRS into Orthogonal Frequency-Division Multiplexing (OFDM) systems. For example, \cite{Yang2020} further enhances time diversity by dynamic passive beamforming that varies IRS over consequent time slots, which enables flexible resource allocation over time-frequency Resource Blocks (RBs). In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency \cite{Dai2020}.
		\end{subsection}

@@

			\textit{Notations:} Scalars are denoted by italic letters, vectors are denoted by bold lower-case letters, and matrices are denoted by bold upper-case letters. $\mathbb{C}^{x \times y}$ denotes the subspace spanned by complex $x \times y$ matrices. $\Re\{\cdot\}$ and $\Im\{\cdot\}$ stand for the real and imaginary part of a complex number or variable, respectively. $(\cdot)^*$, $(\cdot)^T$ and $(\cdot)^H$ represent the conjugate, transpose, and conjugate transpose operators, respectively. $\mathcal{A}\{\cdot\}$ extracts the DC component of a signal, and $\mathcal{E}_X\{\cdot\}$ takes the expectation over the distribution of the random variable $X$ ($X$ may be omitted for simplicity). For a scalar $x$, $\lvert{x}\rvert$ denotes its absolute value. For a vector $\boldsymbol{x}$, $\lVert{\boldsymbol{x}}\rVert$ refers to its Euclidean norm, $\arg(\boldsymbol{x})$ refers to its argument vector, and $\mathrm{diag}(\boldsymbol{x})$ refers to a square diagonal matrix with the elements of $\boldsymbol{x}$ on the main diagonal. For a general matrix $\boldsymbol{M}$, $\mathrm{rank}(\boldsymbol{M})$ denotes it rank. For a square matrix $S$, $\mathrm{Tr}(\boldsymbol{S})$ denotes its trace, and $\boldsymbol{S} \succeq 0$ means that $\boldsymbol{S}$ is positive semi-definite. The distribution of a Circularly Symmetric Complex Gaussian (CSCG) random vector with mean vector $\boldsymbol{\mu}$ and covariance matrix $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{\mu},\boldsymbol{\Sigma})$ and $\sim$ stands for "distributed as". We also denote $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ as stationary solution and solution at iteration $i$, respectively.
		\end{subsection}
	\end{section}

@@

		As shown in Fig.~\ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands with center frequency $f_n$ ($n=1,\dots,N$). Perfect Channel State Information (CSI) with negligible training overhead is assumed to explore the upper bound of the proposed design. A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged. Two practical co-located receiver architectures are compared in terms of R-E region. Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT). In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and IRS design. Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted. We also assume the noise is too small to harvest.

		\begin{subsection}{Transmit Signal}
			Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$, which follows a capacity-achieving i.i.d. CSCG distribution with zero mean and unit variance, namely $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$. The superposed transmit signal on antenna $m$ ($m=1,\dots,M$) at time $t$ is
			\begin{equation}\label{eq:x_m}
				x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{I,n,m}\tilde{x}_{I,n}(t)}+w_{P,n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			where $w_{I/P,n,m}$ denotes the weight on the information and power signal transmitted by antenna $m$ at subband $n$. Define $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ by stacking up weights across all antennas. Therefore, the transmit information and power signals write as
			\begin{align}
				\boldsymbol{x}_{I}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t){e^{j2{\pi}{f_n}{t}}}\right\}}\label{eq:x_I}\\
				\boldsymbol{x}_{P}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}}\label{eq:x_P}
			\end{align}
		\end{subsection}

		\begin{subsection}{Composite Channel}
			At subband $n$, denote the AP-user direct channel as $\boldsymbol{h}_{D,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{R,n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection amplitude $\gamma_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$ \footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\gamma_l=1 \ \forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. On top of this, the IRS matrix collects the reflection coefficients onto the main diagonal entries as $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$. The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection, and IRS-user reflective channel. On top of this, the total composite channel is obtained by superposing the IRS-aided extra channel to the AP-user direct channel as
			\begin{equation}\label{eq:h_n}
				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{D,n}^H + \boldsymbol{h}_{R,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
			\end{equation}
			where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$. Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
		\end{subsection}

		\begin{subsection}{Receive Signal}
			At the single-antenna receiver, the total received signal $y(t)=y_I(t)+y_P(t)$ captures the contribution of information and power components over $N$ subbands, where
			\begin{align}\label{eq:y_IP}
				y_{I}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\\
				y_{P}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}
			\end{align}
		\end{subsection}

		\begin{subsection}{Information Decoder}
			A major benefit of the superposed waveform is that the determined power waveform creates no interference to the information waveform. Therefore, the achievable rate writes as
			\begin{equation}\label{eq:R}
				R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}
			\end{equation}
			where $\rho$ is the power splitting ratio for the energy harvester, $\sigma_n^2$ is the variance of the total noise (RF-band and RF-to-baseband conversion) on tone $n$. Rate \ref{eq:R} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
		\end{subsection}

@@

			Rectifiers consist of nonlinear components as diode and capacitor to produce DC output and store energy \cite{Hagerty2004,Pinuela2013}. Consider a simplified rectifier in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load. Denote $i_s$ as the reverse bias saturation current, $n'$ as the diode ideality factor, $v_t$ as the thermal voltage, $v_d(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the output voltage across the load. A Taylor expansion of the diode characteristic equation $i_d(t)=i_s(e^{v_d(t)/n' v_t}-1)$ around a quiescent operating point $a$ writes as $i_d(t)=\sum_{i=0}^{\infty}k_i'(v_d(t)-a)^i$, where $k_0'=i_s(e^{a/n' v_t}-1)$ and $k_i'=i_se^{a/n'v_t}/i!(n'v_t)^i$ for $i=1,\dots,\infty$. Note that this small-signal expansion model is only valid for the non-linear operation region, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}. Also, an ideal low-pass filter with steady-state response can provide a constant $v_{\text{out}}$ that depends on the peak of $v_{\text{in}}(t)$ \cite{Curty2005}. Therefore, a proper choice of the operating voltage drop is $a=\mathcal{E}\{v_d(t)\}=-v_{\text{out}}$ such that
			\begin{equation}\label{eq:i_d}
				i_d(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i
			\end{equation}

			By discarding the non-DC components, taking expectation over symbol distribution, and truncating \ref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as
			\begin{equation}\label{eq:i_out}
				i_{\text{out}}(t)=\mathcal{A}\{i_d(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}
			\end{equation}

			With the assumption of evenly-spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms has no contribution to DC output. However, $k_i'$ is still a function of $i_{\text{out}}$, and \cite{Clerckx2016a} proved that maximizing a truncated $i_{\text{out}}$ is equivalent to maximizing a monotonic function
			\begin{equation}\label{eq:z}
				z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y(t)^i\right\}\right\}}
			\end{equation}
			where $k_i=i_s/i!(nv_t)^i$. It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \ref{eq:z} with $n_0=2$. However, due to the coupling among different frequencies, some high-order terms also cancel out non-DC components thus contribute to the output DC power. In other words, even terms with $i \ge 4$ account for the nonlinear behavior of the diode. For simplicity, we let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$ and choose $n_0=4$ to investigate fundamental nonlinearity. Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.

>>>>

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation. Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Wu2019}. Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting.	In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel through each reflector with the others switched off. To reduce estimation overhead and design complexity, \cite{Yang2019} exploited the spatial correlation and proposed a group-based IRS model where adjacent elements share a common reflection coefficient. Recent research also explored the possibility of integrating IRS into Orthogonal Frequency-Division Multiplexing (OFDM) systems. For example, \cite{Yang2020} further enhances time diversity by dynamic passive beamforming that varies IRS over consequent time slots, which enables flexible resource allocation over time-frequency Resource Blocks (RBs). In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
		\end{subsection}

@@

			\textit{Notations:} Scalars are denoted by italic letters, vectors are denoted by bold lower-case letters, and matrices are denoted by bold upper-case letters. $j$ refers to the imaginary unit. $\mathbb{C}^{x \times y}$ denotes the subspace spanned by complex $x \times y$ matrices. $\Re\{\cdot\}$ and $\Im\{\cdot\}$ stand for the real and imaginary part of a complex number or variable, respectively. $(\cdot)^*$, $(\cdot)^T$ and $(\cdot)^H$ represent the conjugate, transpose, and conjugate transpose operators, respectively. $\mathcal{A}\{\cdot\}$ extracts the DC component of a signal, and $\mathcal{E}_X\{\cdot\}$ takes the expectation over the distribution of the random variable $X$ ($X$ may be omitted for simplicity). For a scalar $x$, $\lvert{x}\rvert$ denotes its absolute value. For a vector $\boldsymbol{x}$, $\lVert{\boldsymbol{x}}\rVert$ refers to its Euclidean norm, $\arg(\boldsymbol{x})$ refers to its argument vector, and $\mathrm{diag}(\boldsymbol{x})$ refers to a square diagonal matrix with the elements of $\boldsymbol{x}$ on the main diagonal. For a general matrix $\boldsymbol{M}$, $\mathrm{rank}(\boldsymbol{M})$ denotes it rank. For a square matrix $S$, $\mathrm{Tr}(\boldsymbol{S})$ denotes its trace, and $\boldsymbol{S} \succeq 0$ means that $\boldsymbol{S}$ is positive semi-definite. The distribution of a Circularly Symmetric Complex Gaussian (CSCG) random vector with mean vector $\boldsymbol{\mu}$ and covariance matrix $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{\mu},\boldsymbol{\Sigma})$ and $\sim$ stands for "distributed as". We also denote $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ as stationary solution and solution at iteration $i$, respectively.
		\end{subsection}
	\end{section}

@@

		As shown in Fig.~\ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands with center frequency $f_n$ ($n=1,\dots,N$). Perfect Channel State Information (CSI) of all channels are assumed at the AP. A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged. Two practical co-located receiver architectures are compared in terms of R-E region. Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT). In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and IRS design. Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted. We also assume the noise power is too small to be harvested.

		\begin{subsection}{Transmit Signal}
			Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$, which follows an i.i.d. CSCG distribution with zero mean and unit variance, namely $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$. The superposed transmit signal on antenna $m$ ($m=1,\dots,M$) at time $t$ is
			\begin{equation}\label{eq:x_m}
				x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{I,n,m}\tilde{x}_{I,n}(t)}+w_{P,n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			where $w_{I/P,n,m}$ denotes the weight of the information and power signal transmitted by antenna $m$ at subband $n$. Define $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ by stacking up weights across all antennas. Therefore, the transmit information and power signals write as
			\begin{align}
				\boldsymbol{x}_{I}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t){e^{j2{\pi}{f_n}{t}}}\right\}}\,,\label{eq:x_I}\\
				\boldsymbol{x}_{P}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}}\,.\label{eq:x_P}
			\end{align}
		\end{subsection}

		\begin{subsection}{Composite Channel}
			At subband $n$, denote the AP-user direct channel as $\boldsymbol{h}_{D,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{R,n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection amplitude $\gamma_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\gamma_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. Define the IRS matrix as $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries. The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel. Hence, the total composite channel is obtained by superposing the IRS-aided extra channel to the AP-user direct channel as
			\begin{equation}\label{eq:h_n}
				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{D,n}^H + \boldsymbol{h}_{R,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
			\end{equation}
			where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$. Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
		\end{subsection}

		\begin{subsection}{Receive Signal}
			At the single-antenna receiver, the total received signal $y(t)=y_I(t)+y_P(t)$ captures the contribution from information and power components over $N$ subbands, where
			\begin{align}
				y_{I}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\,,\label{eq:y_I}\\
				y_{P}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}\,.\label{eq:y_P}
			\end{align}
		\end{subsection}

		\begin{subsection}{Information Decoder}
			A major benefit of the superposed waveform is that the multisine power waveform creates no interference to the information waveform. Therefore, the achievable rate writes as
			\begin{equation}\label{eq:R}
				R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}
			\end{equation}
			where $\rho$ is the power splitting ratio for the energy harvester, $\sigma_n^2$ is the variance of the total noise (RF-band and RF-to-baseband conversion) on tone $n$. Rate \ref{eq:R} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
		\end{subsection}

@@

			Rectifiers consist of nonlinear components as diode and capacitor to produce DC output and store energy \cite{Hagerty2004,Pinuela2013}. Consider a simplified rectifier in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load. Denote $i_s$ as the reverse bias saturation current, $n'$ as the diode ideality factor, $v_t$ as the thermal voltage, $v_d(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the output voltage across the load. A Taylor expansion of the diode characteristic equation $i_d(t)=i_s(e^{v_d(t)/n' v_t}-1)$ around a quiescent operating point $a$ writes as $i_d(t)=\sum_{i=0}^{\infty}k_i'(v_d(t)-a)^i$, where $k_0'=i_s(e^{a/n' v_t}-1)$ and $k_i'=i_se^{a/n'v_t}/i!(n'v_t)^i$ for $i=1,\dots,\infty$. Note that this small-signal expansion model is only valid for the non-linear operation region, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}. Also, an ideal low-pass filter with steady-state response can provide a constant $v_{\text{out}}$ that depends on the peak of $v_{\text{in}}(t)$ \cite{Curty2005}. Therefore, a proper choice of the operating voltage drop is $a=\mathcal{E}\{v_d(t)\}=-v_{\text{out}}$ such that
			\begin{equation}\label{eq:i_d}
				i_d(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i\,.
			\end{equation}
			By discarding the non-DC components, taking expectation over symbol distribution, and truncating \ref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as
			\begin{equation}\label{eq:i_out}
				i_{\text{out}}(t)=\mathcal{A}\{i_d(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}\,.
			\end{equation}
			With the assumption of evenly-spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms have no contribution to DC output. However, $k_i'$ is still a function of $i_{\text{out}}$, and \cite{Clerckx2016a} proved that maximizing a truncated $i_{\text{out}}$ is equivalent to maximizing a monotonic function
			\begin{equation}\label{eq:z}
				z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y(t)^i\right\}\right\}}
			\end{equation}
			where $k_i=i_s/i!(nv_t)^i$. It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \ref{eq:z} with $n_0=2$. However, due to the coupling among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power. In other words, even-order terms with $i \ge 4$ account for the nonlinear behavior of the diode. For simplicity, we let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$ and choose $n_0=4$ to investigate fundamental nonlinearity. Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current. The corresponding $z$ is detailed in \ref{eq:z_expand}.

			Inspired by \cite{Huang2017}, we stack up channel and waveform vectors over all subbands as $\boldsymbol{h}=[\boldsymbol{h}_1^H,\dots,\boldsymbol{h}_N^H]^H \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^H,\dots,\boldsymbol{w}_{I/P,N}^H]^H \in \mathbb{C}^{MN \times 1}$. Moreover, define $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and let $\boldsymbol{W}_{I/P,n}$ keep its $n$-th ($n=-N+1,\dots,N-1$) block diagonal and null the remaining entries, where the blocks are of size $M \times M$. On top of this, relevant DC terms are expressed in \ref{eq:y_I2} -- \ref{eq:y_P4}.
			\begin{figure*}[b]
				\hrule
				\begin{equation}
					z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho) = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)\,.\label{eq:z_expand}
				\end{equation}
				\hrule
				\begin{flalign}
					\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h}\,,&&\label{eq:y_I2}\\
					\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}
					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2\,,&&\label{eq:y_I4}
				\end{flalign}
				\begin{align}
					\mathcal{A}\left\{y_{P}^2(t)\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h}\,,\label{eq:y_P2}\\
					\mathcal{A}\left\{y_{P}^4(t)\right\}
					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H} = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})^H\,.\label{eq:y_P4}
				\end{align}
			\end{figure*}
		\end{subsection}

		\begin{subsection}{Rate-Energy Region}
			The achievable R-E region is defined as
			\begin{align}
				C_{R_{\text{ID}}-I_{\text{EH}}}(P)
				&\triangleq \biggl\{(R_{\text{ID}}, I_{\text{EH}}): R_{\text{ID}} \le R, I_{\text{EH}} \le z,\nonumber\\
				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_I}\rVert^2+\lVert{\boldsymbol{w}_P}\rVert^2\right) \le P\biggr\}
			\end{align}
			where $P$ is the average transmit power budget and the coefficient \num{1/2} converts the peak power of sine waves to the average power.
		\end{subsection}
	\end{section}

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize the R-E region through a current maximization problem subject to transmit power, IRS magnitude, and different rate constraints
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_I}\rVert^2+\lVert{\boldsymbol{w}_P}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1\,.}
		\end{maxi!}
		Problem~\ref{op:original} is intricate due to non-convex objective function \ref{ob:original} and rate constraint \ref{co:original_rate} with coupled variables. To reduce the design complexity, we propose a suboptimal AO algorithm that iteratively updates the IRS phase shift and transmit waveform plus the receive splitting ratio until convergence.

		\begin{subsection}{IRS Phase Shift}
			In this section, the IRS phase shift $\boldsymbol{\phi}$ is optimized for any given waveform $\boldsymbol{w}_{I/P}$ and splitting ratio $\rho$. We observe that
				\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2
				& = \boldsymbol{w}_{I,n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}\nonumber\\
				& = \boldsymbol{w}_{I,n}^H(\boldsymbol{h}_{D,n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\nonumber\\
				& = \boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{I,n}\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
